A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-05-22 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Break apart LaTeX for arXiv style
Separate the main text body (cwp-main.tex) from the LaTeX for
the specific document class used for sumbission to arXiv in
JHEP style

@@

% CSBS template
\documentclass[twocolumn]{svjour3}          % twocolumn
\smartqed  % flush right qed marks, e.g. at end of proof
\journalname{CSBS}

\usepackage{graphicx}
\usepackage{subcaption}
\captionsetup{compatibility=false}
%\usepackage{subfigure}
\usepackage[titletoc]{appendix}
\usepackage{xspace}
\usepackage{hyperref}

\usepackage[utf8]{inputenc}

\usepackage[style=numeric-comp,sorting=none]{biblatex}
\addbibresource{cwp.bib}
\addbibresource{cwp-chapters.bib}

%% Comment out before final submission
\usepackage{lineno}  % for line numbering during review
\linenumbers

\begin{document}

\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-CWP-2017-01 \\
 & & December 15, 2017 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{2.0cm}

\title{A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s}

%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{HEP Software Foundation (authors are listed at the end of this report)}

%\author{First Author         \and
%        Second Author %etc.
%}

%\authorrunning{Short form of author list} % if too long for running head

%\institute{F. Author \at
%              first address \\
%              Tel.: +123-45-678910\\
M              Fax: +123-45-678910\\
%              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
%           \and
%           S. Author \at
%              second address
%}

\date{Received: date / Accepted: date}

\maketitle

\abstract{Particle physics has an ambitious and broad experimental
programme for the coming decades. This programme requires large
investments in detector hardware, either to build new facilities
and experiments, or to upgrade existing ones.
Similarly, it requires commensurate investment in the R\&D of software to acquire, manage, process,
and analyse the shear amounts of data to be recorded.
In planning for the HL-LHC in particular, it is critical that all of the
collaborating stakeholders agree on the software goals and priorities,
and that the efforts complement each other. In this spirit, this white paper
describes the R\&D activities required to prepare for this software upgrade.}

\newpage

@@

\sloppy
\raggedright
\clearpage
\printbibliography[title={References},heading=bibintoc]

\clearpage
\section*{The HEP Software Foundation}
\input{authors.tex}

\end{document}

>>>>

% This is the main body text for the HSF Community White Paper

@@

@@
